### 2015-06-06 chapters/ipa_meets_unicode.tex
update section names
updated IPA code block pitfall

\section{The International Phonetic Alphabet}
\label{the-international-phonetic-alphabet}

@@

The ambivalent nature of IPA glyphs arises because, on the one hand, the IPA
uses Latin-based glyphs like , or . From this perspective, the IPA seems to be
just another orthographic tradition using Latin characters, all of which do not
get a special treatment within the Unicode Standard (just like e.g.~the French,
German, or Danish orthographic traditions do not have a special status). On the
other hand, the IPA uses many special symbols (like turned , mirrored and/or
extended Latin glyphs ) not found in any other Latin-based writing system. For
this reason, and already in the first version of the Unicode Standard (Version
1.0 from 1991), a special block with code points, called \textsc{IPA Extensions}
was included. As noted in Section 4, Pitfall 1, the Unicode Standard code space
is subdivided into character blocks, which generally encode characters from a
single script. However, as is illustrated by the IPA, characters that form a
single writing system may be dispersed across several different character
blocks. With its diverse collection of symbols from various scripts and
diacritics, the IPA is spread across over 13 blocks in the Unicode
Standard:\footnote{This number of blocks depends on whether only IPA-sanctioned
symbols are counted or if the phonetic symbols commonly found in the literature
are also included, see Moran 2012, Appendix C.}

\begin{itemize}
	\item Basic Latin (30 characters), e.g. <a, b, c, d, e> 
	\item Latin-1 Supplement (4 characters): <æ, ç, ð, ø\textgreater{} 
	\item Latin Extended-A (3 characters): <ħ, ŋ, œ> 
	\item Latin Extended-B (5 characters): <ǀ, ǁ, ǂ, ǃ, ȵ> 
	\item IPA Extensions (70 characters), e.g.: <ɐ, ɑ, ɔ> 
	\item Spacing Modifier Letters (20 characters), e.g.: <ʰ ʷ ˥> 
	\item Combining Diacritical Marks (33 characters), e.g.: <̝ ̥ ̪> 
	\item Greek and Coptic (3 characters): <β, θ, χ> 
	\item Phonetic Extensions (2 characters): <ᴅ, ᴴ> 
	\item Phonetic Extensions Supplement (3 characters): <ᶑ , ᶾ, ᶣ> 
	\item Superscripts and Subscripts (1 character): <ⁿ> 
	\item Arrows (2 characters): \textless{}↑, ↓\textgreater{} 
	\item Latin Extended-C (1 character): <ⱱ> 
\end{itemize}

@@

\section{Pitfall: Ligature and digraphs}
\label{pitfall-ligatures-digraphs}

>>>>

\section{The International Phonetic Alphabet (IPA)}
\label{the-international-phonetic-alphabet}

@@

The ambivalent nature of IPA glyphs arises because, on the one hand, the IPA
uses Latin-based glyphs like <a>, <b> or <p>. From this perspective, the IPA
seems to be just another orthographic tradition using Latin characters, all of
which do not get a special treatment within the Unicode Standard (just like
e.g.~the French, German, or Danish orthographic traditions do not have a special
status). On the other hand, the IPA uses many special symbols (like turned,
mirrored and/or extended Latin glyphs) not found in any other Latin-based
writing system. For this reason, and already in the first version of the Unicode
Standard (Version 1.0 from 1991), a special block with code points, called
\textsc{IPA Extensions} was included.

As explained in Section~\ref{pitfall-blocks}, the Unicode Standard code space is
subdivided into character blocks, which generally encode characters from a
single script. However, as is illustrated by the IPA, characters that form a
single writing system may be dispersed across several different character
blocks. With its diverse collection of symbols from various scripts and
diacritics, the IPA is spread across 13 blocks in the Unicode
Standard:\footnote{This number of blocks depends on whether only IPA-sanctioned
symbols are counted or if the phonetic symbols commonly found in the literature
are also included, see \cite[Appendix C]{Moran2012}}
\begin{itemize}
	\item Basic Latin (30 characters), e.g. <a b c d e \ldots> 
	\item Latin-1 Supplement (4 characters): <æ ç ð ø> 
	\item Latin Extended-A (3 characters): <ħ ŋ œ> 
	\item Latin Extended-B (5 characters): <ǀ ǁ ǂ ǃ ȵ> 
	\item IPA Extensions (70 characters), e.g. <ɐ ɑ ɔ \ldots> 
	\item Spacing Modifier Letters (20 characters), e.g. <ʰ ʷ ˥ \ldots> 
	\item Combining Diacritical Marks (33 characters), e.g. <{\large \ \ ̝\ \ ̥\ \ ̪ }\ldots> 
	\item Greek and Coptic (3 characters): <β θ χ> 
	\item Phonetic Extensions (2 characters): <{\small \fontspec{CharisSIL}ᴅ ᴴ}> 
	\item Phonetic Extensions Supplement (3 characters): <{\small \fontspec{CharisSIL}ᶑ ᶾ ᶣ}> 
	\item Superscripts and Subscripts (1 character): <ⁿ> 
	\item Arrows (4 characters): <↑ ↓ ↗ ↘>
	\item Latin Extended-C (1 character): <{\small \fontspec{CharisSIL}ⱱ}> 
\end{itemize}

@@

\section{Pitfall: Ligatures and digraphs}
\label{pitfall-ligatures-digraphs}
